---
title: "P8105 Homework 1"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```


# Problem 1

The code chunk below creates a data frame comprised of a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”. It also finds the mean of each variable in the data frame.

```{r}
df = tibble(
  vec_norm = rnorm(10),
  vec_logical = vec_norm > 0,
  vec_char = c("My", "name", "is", "Yihan", "Qiu", "and", "I'm", "a", "graduate", "student"),
  vec_factor = factor(c("Asian", "White", "Black", "Asian", "White", "Black", "Asian", "White", "Black", "Asian"))
)
df
```

The code chunk below finds the mean of each variable in the data frame.

```{r}
## Takes the mean of the random sample and it works
mean_vec_norm = mean(pull(df,vec_norm))
mean_vec_norm

## Takes the mean of the logical vector and it works
mean_vec_logical = mean(pull(df, vec_logical))
mean_vec_logical

## Takes the mean of the character vector and it doesn't work
mean_vec_char = mean(pull(df, vec_char))
mean_vec_char

## Takes the mean of the vector factor and it doesn't work
mean_vec_factor = mean(pull(df, vec_factor))
mean_vec_factor
```

The code chunk below tries to convert variables from one type to another.

```{r, eval = FALSE}
## Convert logical variable into numeric
as.numeric(pull(df, vec_logical))

## Convert character variable into numeric
as.numeric(pull(df, vec_char))

## Convert factor variable into numeric
as.numeric(pull(df, vec_factor))
```

We succeeded when trying to convert logical and factor variables into numeric, but we failed when trying to convert character variable into numeric. This suggests that function as.numeric() may not be applicable to character variables. It helps explain what happened when trying to take the mean of each variable as function mean() is only applicable to numeric or logical variables.


# Problem 2

The code chunk below loads the 'penguins' dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

The code chunk below modifies the penguin dataset by eliminating NAs from
flipper_length_mm.

```{r}
penguin_modified = drop_na(penguins, flipper_length_mm)
```

The names of important variables are `r names(penguins)`.

The size of the dataset is `r nrow(penguins)` x `r ncol(penguins)`.

The mean flipper length is `r mean(pull(penguin_modified, flipper_length_mm))`.


The code chuk below makes a scatterplot of flipper length and bill length and saves it.

```{r}
x = pull(penguins, flipper_length_mm)
y = pull(penguins, bill_depth_mm)
plot_df = tibble(x,y)

## A colored scatterplot of flipper length (x) and bill depth (y).
ggplot(plot_df, aes(x = x, y = y, color = pull(penguins,species))) + geom_point()

## Save the scatterplot
ggsave("scatterplot.pdf")
```

